Development of a Reinforcement Learning Enabled Cattle Tracker Prototype

### 2025-02-13 paper/main.tex
Conclusion & Abstract added. Ref reformatted.

\begin{abstract}
This is just a sample \LaTeX template. As usual, most of the customization for the proceedings is done in the \texttt{cai.cls} file. 
\end{abstract}

% add your keywords
\begin{keywords}{Keywords:}
Internet of Things (IoT), reinforcement learning.
\end{keywords}
\copyrightnotice

>>>>

\begin{abstract}
The increasing demand for precision livestock monitoring has led to the development of Internet of Things (IoT)-enabled solutions for real-time tracking and health assessment of cattle. In this study, we present the development of a reinforcement learning-enabled cattle tracker prototype designed to optimize power consumption while ensuring continuous data collection and transmission. The prototype integrates IoT sensors, solar power harvesting, and reinforcement learning-based decision-making to dynamically balance data transmission, storage, and energy conservation. 
The reinforcement learning agent autonomously determines the optimal transmission schedule based on power availability, maximizing data efficiency while prolonging battery life. Experimental evaluations demonstrate the prototype's capability to sustain long-term operation under real-world environmental constraints. The results highlight the feasibility of integrating machine learning with IoT devices for adaptive, energy-efficient cattle monitoring.
Our findings contribute to the broader field of smart agriculture by demonstrating how reinforcement learning can be leveraged to enhance IoT-based livestock management. Future work will focus on optimizing the decision-making model for diverse environmental conditions and scaling the system for larger deployments.

\end{abstract}

% add your keywords
\begin{keywords}{Keywords:}
Internet of Things (IoT), Reinforcement Learning, Cattle Monitoring.
\end{keywords}
\copyrightnotice
